---
title: "map_layer_selection"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{map_layer_selection}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

```{r setup}
library(mapselector)
```


```{r}
library(dplyr)
library(leaflet)

data <- data.frame(Name = c("A", "A", "A", "B", "B", "C", "C", "C"),
                   Value1 = c(12,43,54,34,23,77,44,22),
                   Value2 = c(6,5,2,7,5,6,4,3),
                   Lat = c(51.1, 51.6, 57.3, 52.4, 56.3, 54.3, 60.4, 49.2),
                   Lon = c(5, -3, -2, -1, 4, 3, -5, 0))
data %>%
  leaflet() %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addCircles(lat=~Lat, lng=~Lon, radius = ~Value1*1000, group=c(~Name, "Value1")) %>%
  addCircles(lat=~Lat, lng=~Lon, radius = ~Value2, group=c(~Name, "Value2")) %>%
  addLayersControl(
    baseGroups = c("Value1", "Value2"),
    overlayGroups = c("A", "B", "C"),
    options = layersControlOptions(collapsed = F)
  )


## Stackoverflow

library(dplyr)
library(leaflet)
library(htmlwidgets)

data <- data.frame(ID = c("1", "2","3","4","5","6","7","8"),
                   Name = c("A", "A", "A", "B", "B", "C", "C", "C"),
                   Value1 = c(12,43,54,34,23,77,44,22),
                   Value2 = c(6,5,2,7,5,6,4,3),
                   Lat = c(51.1, 51.6, 57.3, 52.4, 56.3, 54.3, 60.4, 49.2),
                   Lon = c(5, -3, -2, -1, 4, 3, -5, 0))
data %>%
  leaflet() %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addCircles(lat=~Lat, lng=~Lon, radius = ~Value1*1000, group=~Name, label=~Name, popup=~as.character(Value1), layerId = ~paste(ID,"Value1", sep="")) %>%
  addCircles(lat=~Lat, lng=~Lon, radius = ~Value2*5000, group=~Name, label=~Name, popup=~as.character(Value2), layerId = ~paste(ID,"Value2", sep="")) %>%
  addLayersControl(
    baseGroups = c("Value1", "Value2"),
    overlayGroups = c("A", "B", "C"),
    options = layersControlOptions(collapsed = F)
  ) %>%
  htmlwidgets::onRender("
    function(el, x) {
      var myMap = this;
      var baseLayer = 'Value1';
      myMap.eachLayer(function(layer){
        var id = layer.options.layerId;
        if (id){
          if ('Value1' !== id.substring(1,)){
            layer.getElement().style.display = 'none';
          }
        }
      })
      console.log(myMap.baselayer);
      myMap.on('baselayerchange',
        function (e) {
          baseLayer=e.name;
          myMap.eachLayer(function (layer) {
              var id = layer.options.layerId;
              if (id){
                if (e.name !== id.substring(1,)){
                  layer.getElement().style.display = 'none';
                  layer.closePopup();
                }
                if (e.name === id.substring(1,)){
                  layer.getElement().style.display = 'block';
                }
              }

          });
        })
        myMap.on('overlayadd', function(e){
          myMap.eachLayer(function(layer){
            var id = layer.options.layerId;
            if (id){
                if (baseLayer !== id.substring(1,)){
                  layer.getElement().style.display = 'none';
                }
            }    
          })
        })
    }")

```


Now observe this example from the Shiny page:

```{r rstudio-example}
library(shiny)
library(leaflet)
library(RColorBrewer)

ui <- bootstrapPage(
  tags$style(type = "text/css", "html, body {width:100%;height:100%}"),
  leafletOutput("map", width = "100%", height = "100%"),
  absolutePanel(top = 10, right = 10,
    sliderInput("range", "Magnitudes", min(quakes$mag), max(quakes$mag),
      value = range(quakes$mag), step = 0.1
    ),
    selectInput("colors", "Color Scheme",
      rownames(subset(brewer.pal.info, category %in% c("seq", "div")))
    ),
    checkboxInput("legend", "Show legend", TRUE)
  )
)

server <- function(input, output, session) {

  # Reactive expression for the data subsetted to what the user selected
  filteredData <- reactive({
    quakes[quakes$mag >= input$range[1] & quakes$mag <= input$range[2],]
  })

  # This reactive expression represents the palette function,
  # which changes as the user makes selections in UI.
  colorpal <- reactive({
    colorNumeric(input$colors, quakes$mag)
  })

  output$map <- renderLeaflet({
    # Use leaflet() here, and only include aspects of the map that
    # won't need to change dynamically (at least, not unless the
    # entire map is being torn down and recreated).
    leaflet(quakes) %>% addTiles() %>%
      fitBounds(~min(long), ~min(lat), ~max(long), ~max(lat))
  })

  # Incremental changes to the map (in this case, replacing the
  # circles when a new color is chosen) should be performed in
  # an observer. Each independent set of things that can change
  # should be managed in its own observer.
  observe({
    pal <- colorpal()

    leafletProxy("map", data = filteredData()) %>%
      clearShapes() %>%
      addCircles(radius = ~10^mag/10, weight = 1, color = "#777777",
        fillColor = ~pal(mag), fillOpacity = 0.7, popup = ~paste(mag)
      )
  })

  # Use a separate observer to recreate the legend as needed.
  observe({
    proxy <- leafletProxy("map", data = quakes)

    # Remove any existing legend, and only if the legend is
    # enabled, create a new one.
    proxy %>% clearControls()
    if (input$legend) {
      pal <- colorpal()
      proxy %>% addLegend(position = "bottomright",
        pal = pal, values = ~mag
      )
    }
  })
}

shinyApp(ui, server)
```


First, put the example from SO into a similar Shiny app structure

```{r}

library(shiny)
library(leaflet)
library(RColorBrewer)

ui <- bootstrapPage(
  tags$style(type = "text/css", "html, body {width:100%;height:100%}"),
  leafletOutput("map", width = "100%", height = "100%")
)

server <- function(input, output, session) {
  
  data <- data.frame(ID = c("1", "2","3","4","5","6","7","8"),
                     Name = c("A", "A", "A", "B", "B", "C", "C", "C"),
                     Value1 = c(12,43,54,34,23,77,44,22),
                     Value2 = c(6,5,2,7,5,6,4,3),
                     Lat = c(51.1, 51.6, 57.3, 52.4, 56.3, 54.3, 60.4, 49.2),
                     Lon = c(5, -3, -2, -1, 4, 3, -5, 0))
  
  output$map <- renderLeaflet({
    data %>%
      leaflet() %>%
      addProviderTiles(providers$CartoDB.Positron) %>%
      addCircles(lat = ~Lat,
                 lng = ~Lon, 
                 radius = ~Value1*1000,
                 group = ~Name, 
                 label = ~Name,
                 popup = ~as.character(Value1),
                 layerId = ~paste(ID,"Value1", sep=""))
  })
    
}


shinyApp(ui, server)
```

So far so good. now, extend with leafletProxy

```{r}

library(shiny)
library(leaflet)
library(RColorBrewer)

ui <- bootstrapPage(
  tags$style(type = "text/css", "html, body {width:100%;height:100%}"),
  leafletOutput("map", width = "100%", height = "100%"),
  
)

server <- function(input, output, session) {
  
  data_df <- data.frame(ID = c("1", "2","3","4","5","6","7","8"),
                     Name = c("A", "A", "A", "B", "B", "C", "C", "C"),
                     Value1 = c(12,43,54,34,23,77,44,22),
                     Value2 = c(6,5,2,7,5,6,4,3),
                     Lat = c(51.1, 51.6, 57.3, 52.4, 56.3, 54.3, 60.4, 49.2),
                     Lon = c(5, -3, -2, -1, 4, 3, -5, 0))
  
  output$map <- renderLeaflet({
      leaflet(data_df) %>%
      addTiles() %>%
      fitBounds(~min(Lon), ~min(Lat), ~max(Lon), ~max(Lat)) %>% 
      addControl(radioButtons("var_chosen", label = "Which variable?", choices = c("Value 1", "Value 2")),
                 position = "topright")
  })
  
  leafletProxy("map") %>%
      clearShapes() %>% 
      addCircles(lat = ~Lat,
                 lng = ~Lon,
                 radius = ~Value1*1000,
                 group = ~Name,
                 label = ~Name,
                 popup = ~as.character(Value1),
                 data = data_df)
}

shinyApp(ui, server)
```

Now, make an observer of the chosen variable that reveals one type of marker or the other:


```{r}

library(shiny)
library(leaflet)
library(RColorBrewer)

ui <- bootstrapPage(
  tags$style(type = "text/css", "html, body {width:100%;height:100%}"),
  leafletOutput("map", width = "100%", height = "100%")
)

server <- function(input, output, session) {
  
  data_df <- data.frame(ID = c("1", "2","3","4","5","6","7","8"),
                     Name = c("A", "A", "A", "B", "B", "C", "C", "C"),
                     Value1 = c(12,43,54,34,23,77,44,22),
                     Value2 = c(6,5,2,7,5,6,4,3),
                     Lat = c(51.1, 51.6, 57.3, 52.4, 56.3, 54.3, 60.4, 49.2),
                     Lon = c(5, -3, -2, -1, 4, 3, -5, 0))
  
  output$map <- renderLeaflet({
      leaflet(data_df) %>%
      addTiles() %>%
      fitBounds(~min(Lon), ~min(Lat), ~max(Lon), ~max(Lat)) %>% 
      addControl(radioButtons("var_chosen", label = "Which variable?", 
                              choices = c("Value #1" = "Value1",
                                          "Value #2" = "Value2")),
                 position = "topright")
  })
  
  # necessary because (apparently) the control isn't present until the map is
  rv <- reactiveValues(value_chosen = "Value1")
  
  observeEvent(input$var_chosen,{
      rv$value_chosen <- input$var_chosen
    })
  
  rad_reactive <- reactive({
    switch(rv$value_chosen,
           "Value1" = data_df[["Value1"]]*1000,
           "Value2" = data_df[["Value2"]]*5000)
  })
  
  observe({
    leafletProxy("map") %>%
      clearShapes() %>%
      addCircles(lat = ~Lat,
                 lng = ~Lon,
                 radius = rad_reactive(),
                 group = ~Name,
                 label = ~Name,
                 popup = ~as.character(data_df[[rv$value_chosen]]),
                 data = data_df)
  })
}

shinyApp(ui, server)
```


```{r}
downloaded_sites <- rcoleo::download_sites_sf() %>% 
  dplyr::left_join(rcoleo::get_richness(by_site = TRUE),by = c("site_code"))
```


use markers instead of circles, but only for ONE of the variables. or add the category instead. 




```{r switch-markers}

library(shiny)
library(leaflet)
library(RColorBrewer)

ui <- bootstrapPage(
  tags$style(type = "text/css", "html, body {width:100%;height:100%}"),
  leafletOutput("map", width = "100%", height = "100%")
)

server <- function(input, output, session) {
  
  data_df <- data.frame(ID = c("1", "2","3","4","5","6","7","8"),
                     Name = c("toundrique", "toundrique", "toundrique", "lac", "lac", "marais", "marais", "marais"),
                     Value1 = c(12,43,54,34,23,77,44,22),
                     Value2 = c(6,5,2,7,5,6,4,3),
                     Lat = c(51.1, 51.6, 57.3, 52.4, 56.3, 54.3, 60.4, 49.2),
                     Lon = c(5, -3, -2, -1, 4, 3, -5, 0))
  
  output$map <- renderLeaflet({
      leaflet(data_df) %>%
      addTiles() %>%
      fitBounds(~min(Lon), ~min(Lat), ~max(Lon), ~max(Lat)) %>% 
      addControl(radioButtons("var_chosen", label = "Which variable?", 
                              choices = c("Value #1" = "Value1",
                                          "Value #2" = "Value2",
                                          "Name of Type"= "Name")),
                 position = "topright")
  })
  
  # necessary because (apparently) the control isn't present until the map is
  rv <- reactiveValues(value_chosen = "Value1")
  
  observeEvent(input$var_chosen,{
      rv$value_chosen <- input$var_chosen
    })
  
  # if the category is some continuious thing, set the radius of circles to it.
  
  ics <- mapselector::make_site_icons()
  
  rad_reactive <- reactive({
    switch(rv$value_chosen,
           "Value1" = 
             function(x) addCircles(x, 
                                    lat = ~Lat,
                                    lng = ~Lon,
                                    color= "#497e9f",
                                    stroke = TRUE,
                                    weight = 5, 
                                    opacity = 0.75,
                                    radius = data_df[["Value1"]]*1000,
                                    group = ~Name,
                                    label = ~Name,
                                    popup = ~as.character(data_df[["Value1"]]),
                                    data = data_df),
           "Value2" =
             function(x) addCircles(x, lat = ~Lat,
                                    lng = ~Lon,
                                    radius = data_df[["Value2"]]*5000,
                                    group = ~Name,
                                    label = ~Name,
                                    popup = ~as.character(data_df[["Value2"]]),
                                    data = data_df),
           "Name" = 
             function(x) addAwesomeMarkers(x, lat = ~Lat,
                                    lng = ~Lon,
                                    icon = ~ics[Name],
                                    group = ~Name,
                                    label = ~Name,
                                    popup = ~as.character(data_df[["Name"]]),
                                    data = data_df) 
           )
  })
  
  observe({
    req(rad_reactive)
    leafletProxy("map") %>%
      clearShapes() %>%
      clearMarkers() %>% 
      rad_reactive()(.) %>% 
      addLayersControl(overlayGroups=~Name,
                       options = layersControlOptions(collapsed=FALSE),
                       data = data_df)
  })
  
}

shinyApp(ui, server)
```

add a legend with html [as described here](https://stackoverflow.com/questions/37862467/leaflet-legend-for-custom-markers-in-r) ? 
which only appears when you have the categorical thing selected

Convenience function inside to partially complete `addCircles`

create a module that makes this map and spits out the clicked ID. 

```{r with-rcoleo}
downloaded_sites <- rcoleo::download_sites_sf() %>% 
  dplyr::left_join(rcoleo::get_richness(by_site = TRUE),by = c("site_code")) %>% 
  add_site_name_df
  
```

```{r}
library(shiny)
library(leaflet)
library(RColorBrewer)

ui <- bootstrapPage(
  tags$style(type = "text/css", "html, body {width:100%;height:100%}"),
  fa_dependency(),
  leafletOutput("map", width = "100%", height = "100%")
)

server <- function(input, output, session) {
  
  data_df <- drop_empty_campaigns(downloaded_sites) 
  
  choice <- function(m) addControl(m,
                                   radioButtons("var_chosen", 
                                                label = "Montre sur la carte:", 
                                                choices = c("Habitat"           = "type",
                                                            "Combien d'especes" = "richness")),
                                   className = "markerchoice",
                                   position = "topright"
                                   )
  
  output$map <- renderLeaflet({
    make_leaflet_empty() %>% 
      choice(.)
  })
  
  # necessary because (apparently) the control isn't present until the map is
  rv <- reactiveValues(value_chosen = "type")
  
  observeEvent(input$var_chosen,{
      rv$value_chosen <- input$var_chosen
    })
  
  # if the category is some continuious thing, set the radius of circles to it.
  
  ics <- mapselector::make_site_icons()
  
  map_marker_reactive <- reactive({
    switch(rv$value_chosen,
           "richness" = 
             function(x) addCircleMarkers(x,
                                          radius = ~(as.integer(richness)/4),
                                          group = ~type,
                                          color= "#497e9f",
                                          stroke = TRUE,
                                          weight=5, 
                                          opacity = 0.75,
                                           label = ~display_name,
                                           layerId = ~display_name,
                                          data = data_df),
           "type" =
             function(x) addAwesomeMarkers(x,
                                           icon = ~ics[type],
                                           group = ~type,
                                           label = ~display_name,
                                           layerId = ~display_name,
                                           data = data_df) 
    )
  })
  
  observe({
    req(map_marker_reactive)
    leafletProxy("map") %>%
      clearMarkers() %>% 
      map_marker_reactive()(.) %>% 
      addLayersControl(overlayGroups = ~type,
                       options = layersControlOptions(collapsed = FALSE),
                       data = data_df)
  })
  
  observeEvent(input$map_marker_click$id, cat(paste0(input$map_marker_click$id, "\n")))
  
  return(list(
      click = reactive(input$map_marker_click$id)
      ))
}

shinyApp(ui, server)
```

Note that because we use `addCircleMarkers`, both are markers and we only need to use `clearMarkers` to clear them and `map_marker_click`


Do it via a module:

```{r}

ui <- bootstrapPage(
  tags$style(type = "text/css", "html, body {width:100%;height:100%}"),
  fa_dependency(),
  mod_map_richness_campaigns_ui("map_richness_campaigns_1")
)

server <- function(input, output, session) {
  
  userclick <- mod_map_richness_campaigns_server("map_richness_campaigns_1", downloaded_site_name = downloaded_sites)
  
  
  observeEvent(userclick$display_name(), cat(paste0("site name: ", userclick$display_name(), "\n",
                                                    "site code: ", userclick$site_code(), "\n")))
  
}

shinyApp(ui, server)
```



modal click -- or should this output a reactive value or somethign? witht he reactive graph constrained? or, does the modal resetting happen OUTSIDE of the map selection but inside the modal work? 