---
title: "rank_abundance"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{rank_abundance}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(tidyverse)
# start by getting data
# get all data frist 
site_df <- rcoleo::download_sites_sf()
# get one campaign
some_data <- mapselector::get_subset_site(site = site_df,
                            site_code_sel = "137_111_F01")

# combine
some_data_type <- site_df %>% filter(site_code == "137_111_F01") %>% 
  pull(campaigns) %>% # if it was multiple sites, bind_rows here 
  bind_rows() %>% 
  select(id, site_id, type, campaign_id = id) %>% 
  left_join(some_data)


glimpse(some_data)

# no way to tell the kind of campaign just from this? 
some_data %>% 
  count(obs_species.taxa_name)


```


okay probably need a function that adds the "type" info back into the observation table. 


Now need to be able to calculate rank abd for every type

```{r}
some_data_type %>% 
  count(type)
```


```{r}

# drop campaigns with nothing

some_data_list <- some_data_type %>% 
  rename(taxa = obs_species.taxa_name, 
         variable = obs_species.variable,
         value = obs_species.value) %>% 
  split(.$type) %>% 
  discard(~ all(is.na(.$taxa)))
```




## calculating rank abundance curves

### Vege

```{r}
some_data_list$végétation %>% 
  select(taxa, value) %>% 
  dplyr::mutate(rank = rank(value, ties.method = "random"))
```

### acoustique


```{r}
# acoustique
some_data_list$acoustique %>% 
  dplyr::count(taxa, name = "abundance") %>% 
  dplyr::mutate(rank = rank(abundance, ties.method = "random"))
```


### insects sol

```{r}
some_data_list$insectes_sol %>% glimpse
# has different samples!! 

some_data_list$insectes_sol %>% 
  count(campaignId, sampleId, taxa)

```

Ok so there are no duplicates of soil insects unless it is via something called "inconnu".

So first thing we need to do is drop all those. for this simple visualization, lets ignore all the subsamples of a site! 

```{r}
some_data_list$insectes_sol %>% 
  dplyr::filter(taxa != "inconnu", 
         value > 1) %>% 
  dplyr::mutate(taxa = stringr::str_trim(taxa)) %>% 
  dplyr::group_by(taxa) %>% 
  dplyr::summarize(abundance = sum(value)) %>% 
  dplyr::mutate(rank = rank(abundance, ties.method = "random"))
```


OK what about the others?

need a new site:

TODO automate this process and integrate with current workflow.
Perhaps "mod_campaign_type_server" could even include this.

```{r}

site_df <- rcoleo::download_sites_sf()

site_df$campaigns %>% keep(~nrow(.)>0) %>% map_df(~select(., type)) %>% 
  distinct
# okay so there is zoops




some_data <- mapselector::get_subset_site(site = site_df,
                            site_code_sel = "136_116_H01")

camp_info <- site_df %>% filter(site_code == "136_116_H01") %>% 
  pull(campaigns) %>% # if it was multiple sites, bind_rows here 
  bind_rows() %>% 
  select(id, site_id, type, campaign_id = id)

# combine
some_data_type <- camp_info %>% 
  left_join(some_data)


some_data_list <- some_data_type %>% 
  rename(taxa = obs_species.taxa_name, 
         variable = obs_species.variable,
         value = obs_species.value) %>% 
  split(.$type) %>% 
  discard(~ all(is.na(.$taxa)))

```



need to think about how to get all observations of a certain kind from ALL sites. 

related, how to prevent downloading the same thing multiple times? if somebody chooses soil (download) and then odonates (download) and then soil again (don't download)


```{r}
map_at
```


## Notes

### Duplicated soil insects


Oh and are the soil insects doubled somewhere? need to confirm actually.

```{r}
some_data_list$insectes_sol %>% 
  filter(obs_species.taxa_name != "inconnu") %>% 
  select(sampleId, taxa = obs_species.taxa_name) %>% 
  {split(.$taxa, .$sampleId)} %>% map(unique)
```


Here I'm looking for some sign that these are different species lists -- we might have injected the SAMPLES twice, meaning that there would be duplicates at the sample level -- in other words, samples with different IDs but the same species in the same abundances.

dang we need some data validation -- we need to confirm that the invetebrate data corresponds to the spreadsheets that we have from the MFFP.


```{r}
library(tidyverse)
library(rcoleo)
raw_resp <- get_species_site("v")

raw_resp %>% 
  ggplot(aes(y = site_code, x = taxa_name)) + geom_tile()


# okay add the counts and order them

raw_resp %>% 
  filter(!is.na(taxa_name)) %>% 
  add_count(site_code, name = "sn") %>% 
  add_count(taxa_name, name = "tn") %>% 
  mutate(site_code = forcats::fct_reorder(site_code, sn),
         taxa_name = forcats::fct_reorder(taxa_name, tn)) %>% 
ggplot(aes(y = site_code, x = taxa_name)) + geom_tile() + coord_fixed() + theme_classic()


raw_resp %>% count(taxa_name)
```

how to turn this into rank-freq plot

```{r}
rank_species <- raw_resp %>% 
  filter(!is.na(taxa_name)) %>% 
  count(taxa_name) %>% 
  mutate(rank = rank(desc(n), ties.method = "random")) 

rank_species %>% 
  ggplot(aes(x = rank, y = n)) + geom_point() + 
  theme_minimal() + 
  labs(x = "rang des espèces", y = "Frequence des especes")
```



or into rank-richness plot

